Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-20 papers/B1555_EdgeOn/B1555_letter.tex
A bit of rewriting of the intro to the B1555 paper

\section{Introduction}
	To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly. However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way. This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in local universe. Most satellite galaxies are too faint to be directly detected. Futhermore, low-mass dark matter subhaloes may contain too less gas to form stats \citep{P11}. These factors make gravitational effects be powerful and promising tools in the substructure searching.\\   
	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems. This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}. In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band. However, only small number of flux ratio anomalous systems in radio are avaliable for analysis. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis. All of these studies show that flux ratio anomalous lens systems are expected to bring a new insight to our understanding on structure formation.\\
	On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

@@

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code $glafic$ \citep{Oguri} with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with two models. The first model consists of an SIE bulge and an exponential edge-on disk(SIE+Expdisk). The second model consists of two SIE mass profiles, for bulge and disk respectively. The full best-fit parameters are shown in Table 1. Both of these models predict fairly matched results with the radio observation. The comparison of observation and SIE+Expdisk result is in Figure 2, Table 2 \& 3.\\

>>>>

\section{Introduction}

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane.  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}.  In order to understand
this discrepancy, it is imperative to build up a large sample of satellites /
subhalos in galaxies outside the Local Group.  This process is challenging
due to the faintness of the satellite galaxies.  Furthermore, lower-mass
satellites may not be able to retain the gas needed for ongoing star
formation \citep[e.g.,][]{P11}, rendering them effectively dark.
These
factors make gravitational effects be powerful and promising tools in
the substructure searching.

	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems. This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}. In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band. However, only small number of flux ratio anomalous systems in radio are avaliable for analysis. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis. All of these studies show that flux ratio anomalous lens systems are expected to bring a new insight to our understanding on structure formation.\\
	On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

@@

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides an excellent fit to the image positions (?? IS THIS TRUE?) but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk(SIE+Expdisk). The second model
consists of two SIE mass profiles, for bulge and disk
respectively. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
